Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-02-06 output/paper/_figures.qmd
First round of modifications for tables and figures done.
Modified almost all text based on MV. Added authors and roles.

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

>>>>

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

### 2024-02-06 output/paper/_si.qmd
Modified almost all text based on MV. Added authors and roles.

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite, Metabolite, LLOQ)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Lower limits of quantification for the glucocorticosteroids (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::rename(Exposure = "exposure") |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of \acr{edcs}, by cohort (HELIX Study; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
**Measurement classification of the glucocorticosteroids, by cohort (HELIX Study; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOQ; 3, interference or out of range; 4, not detected.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX Study; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

### Sensitivity to exposure assessment

>>>>

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite, Metabolite, LLOQ)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Lower limits of quantification for the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::rename(Exposure = "exposure") |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of \acr{edcs}, by cohort (HELIX subcohort; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
**Measurement classification of the glucocorticosteroids, by cohort (HELIX subcohort; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOQ; 3, interference or out of range; 4, not detected.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

### 2024-02-06 output/paper/_tables.qmd
Modified almost all text based on MV. Added authors and roles.

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
```
**Participant characteristics, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-edc-desc}
```{r edc-desc}
targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```
**Participants endocrine disruptors concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-met-desc}
```{r met-desc}
desc_chems_mets$desc_mets
```
**Participants glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

scores |>
  gtsummary::tbl_summary(
    by = "cohort"
  ) |>
  gtsummary::add_overall() |>
  gtsummary::as_gt() |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-hypothesis-1}
```{r hypothesis-1}
tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on \acr{hitrtse} (HELIX Study; 2013-2016).**
:::

::: {#tbl-hypothesis-2}
```{r hypothesis-2}
tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on the glucocorticosteroids (HELIX Study; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of the glucocorticosteroids on \acr{hitrtse} (HELIX Study; 2013-2016).**
:::

>>>>

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
```
**Participant characteristics, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

::: {#tbl-edc-desc}
```{r edc-desc}
targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```
**Participants endocrine disruptors concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

::: {#tbl-met-desc}
```{r met-desc}
desc_chems_mets$desc_mets
```
**Participants glucocorticosteroids concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

scores |>
  gtsummary::tbl_summary(
    by = "cohort"
  ) |>
  gtsummary::add_overall() |>
  gtsummary::as_gt() |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

::: {#tbl-hypothesis-1}
```{r hypothesis-1}
tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on \acr{hitrtse} (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-2}
```{r hypothesis-2}
tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of the glucocorticosteroids on \acr{hitrtse} (HELIX subcohort; 2013-2016).**
:::
